Something with Objects and Names

### 2019-12-05 papers/ACL2020/experiments.tex
matrices with order error categories

\begin{figure}[t]
\includegraphics[scale=.6]{images/FRCNN_change_matrix.jpg}
\caption{Confusion-matrix-style visualization showing error categories of predictions that changed from object detection with FRCNN-VG1600 to naming with FRCNN-VG1600-VGMN (finetuned)}
\end{figure}

>>>>

\begin{figure*}[t]
\includegraphics[scale=.5]{images/matrix_FRCNN--VG1600_VG_FRCNN--MN442_VG.jpg}
\includegraphics[scale=.5]{images/matrix_FRCNN--VG1600_VG_FRCNN--VG1600--VGMN_MN.jpg}
\includegraphics[scale=.5]{images/matrix_FRCNN--VG1600_VG_ResNet101--VGMN_VG.jpg}
\includegraphics[scale=.5]{images/matrix_FRCNN--VG1600_VG_ResNet101--MN442_MN.jpg}

\caption{Confusion-matrix-style visualization showing error categories of predictions that changed from object detection with FRCNN-VG1600 to naming with FRCNN-VG1600-VGMN (finetuned)}
\end{figure*}
